A Data-Driven Framework for Neural Field Modeling

### 2011-01-03 ltx/first_order_framework/LaTeX_Manuscript.tex
change hz to cycles/mm

\subsection{Spatial Frequency Analysis}
The spectral analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field. Fig.~\ref{fig:Figure4}(A) shows the spatial frequency of the neural field and Fig.~\ref{fig:Figure4}(B) shows the spatial frequency of the reconstructed neural field from the basis function decomposition. The cutoff frequency ($-3$~dB point) of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz. From equation~\ref{eq:MinimumSensorDistance}, this yielded a maximum sensor separation of 2.08~mm. This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to mitigate problems associated with spatial aliasing of the dominant dynamics.

The spatial frequency of the observed field is shown in Fig.~\ref{fig:Figure5}(A). The cutoff frequency is $\boldsymbol{\nu}_{cy} \approx 0.2$~Hz ($-3$~dB point). The observation cutoff frequency is lower than the field cutoff due to the low-pass filtering effect of the sensors. The spatial frequency response of the sensors can be seen in Fig.~\ref{fig:Figure5}(B).

As described in Section~\ref{SpectralAnalysisSection}, the basis function configuration can be systematically chosen to account for the full spatial bandwidth from the observations, or alternatively, the configuration can be chosen to represent the neural field up to a specified bandwidth to limit the computational complexity of the estimation procedure. In the examples provided in this paper, the later option was chosen, where the neural field cutoff frequency was further reduced to $\boldsymbol{\nu}_{c\phi} = 0.12$~Hz. The band-limiting effect on the field reconstruction can be seen by comparing Fig.~\ref{fig:Figure4}(A) to Fig.~\ref{fig:Figure4}(B). This effect is due to the spatial frequency response of the basis functions, which is shown in Fig.~\ref{fig:Figure5}(C). Due to the slow roll-off in the frequency response of Gaussian basis functions an oversampling parameter of $\rho_{\phi} = 1.67$ was chosen. Given the spectral response of the basis functions, the over-sampling parameter, and the spatial domain an equally spaced grid of $9\times9$ basis functions was used to decompose the field, which resulted in $81$ states.

@@

	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & Hz \\
	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & Hz$^2$\\

>>>>

\subsection{Spatial Frequency Analysis}
The spectral analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field. Fig.~\ref{fig:Figure4}(A) shows the spatial frequency of the neural field and Fig.~\ref{fig:Figure4}(B) shows the spatial frequency of the reconstructed neural field from the basis function decomposition. The cutoff frequency ($-3$~dB point) of the neural field is \parham{$\boldsymbol{\nu}_c \approx 0.24$~cycles/mm}. From equation~\ref{eq:MinimumSensorDistance}, this yielded a maximum sensor separation of 2.08~mm. This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to mitigate problems associated with spatial aliasing of the dominant dynamics.

The spatial frequency of the observed field is shown in Fig.~\ref{fig:Figure5}(A). The cutoff frequency is \parham{$\boldsymbol{\nu}_{cy} \approx 0.2$~cycles/mm} ($-3$~dB point). The observation cutoff frequency is lower than the field cutoff due to the low-pass filtering effect of the sensors. The spatial frequency response of the sensors can be seen in Fig.~\ref{fig:Figure5}(B).

As described in Section~\ref{SpectralAnalysisSection}, the basis function configuration can be systematically chosen to account for the full spatial bandwidth from the observations, or alternatively, the configuration can be chosen to represent the neural field up to a specified bandwidth to limit the computational complexity of the estimation procedure. In the examples provided in this paper, the later option was chosen, where the neural field cutoff frequency was further reduced to \parham{$\boldsymbol{\nu}_{c\phi} = 0.12$~cycles/mm}. The band-limiting effect on the field reconstruction can be seen by comparing Fig.~\ref{fig:Figure4}(A) to Fig.~\ref{fig:Figure4}(B). This effect is due to the spatial frequency response of the basis functions, which is shown in Fig.~\ref{fig:Figure5}(C). Due to the slow roll-off in the frequency response of Gaussian basis functions an oversampling parameter of $\rho_{\phi} = 1.67$ was chosen. Given the spectral response of the basis functions, the over-sampling parameter, and the spatial domain an equally spaced grid of $9\times9$ basis functions was used to decompose the field, which resulted in $81$ states.

@@

	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & \parham{cycles/mm} \\
	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & \parham{cycles/mm$^2$}\\
